Abstract

### 2025-10-07 output/Main_text.Rmd
Explain axis labeling in Figure 1

Up to now, all our derivations have considered $`r N_DIMS`$-dimensional spaces;
that is, multidimensional parameters and item vector coordinates
can be computed in an arbitrary large number of dimensions.
However, as plotting more than two dimensions
is difficult on a bidimensional display
(and hardly possible at all for more than three dimensions with the
currently available technology),
we limit ourselves to the bidimensional case here.
The example in Figure \@ref(fig:item-plot-out) showcases a representation of
a set of items in two different bidimensional spaces.
Their parameters are shown in Table \@ref(tab:example-items-table-out),
both in the original `r MODEL_ACRONYM` metric, and in the multidimensional
metric in two different cases, with different latent covariance structures.
In the first case (columns $`r CORR_ORTH_OUT`$),
the two latent dimensions are independent;
in the second one (columns $`r CORR_ORTH_OUT`$),
the correlation between the dimensions is .5.
Note that, although the `r MODEL_ACRONYM` parameters are the same in both cases,
their (correlation-based) multidimensional parameters change when different
correlations are used.

>>>>

Up to now, all our derivations have considered $`r N_DIMS`$-dimensional spaces;
that is, multidimensional parameters and item vector coordinates
can be computed in an arbitrary large number of dimensions.
However, as plotting more than two dimensions
is difficult on a bidimensional display
(and hardly possible at all for more than three dimensions with the
currently available technology),
we limit ourselves to the bidimensional case here.
The example in Figure \@ref(fig:item-plot-out) showcases a representation of
a set of items in two different bidimensional spaces.
(The axes are labelled as $`r TRAIT_COMP_1`$ and $`r TRAIT_COMP_2`$
for simplicity, but note that they represent the coordinates of
a latent trait point transformed to the test space,
that is, $`r TRAIT_COORD_1`$ and  $`r TRAIT_COORD_2`$.)
Their parameters are shown in Table \@ref(tab:example-items-table-out),
both in the original `r MODEL_ACRONYM` metric and
in the multidimensional metric,
in two different cases with different latent covariance structures.
In the first case (columns $`r CORR_ORTH_OUT`$),
the two latent dimensions are independent;
in the second one (columns $`r CORR_ORTH_OUT`$),
the correlation between the dimensions is .5.
The same `r MODEL_ACRONYM` parameters are used in both cases,
but their (correlation-based) multidimensional parameters change when different
correlations are used.
